### 2019-04-11 paper/paper.tex
formatted and edited Greg's github data paragraph

\textbf{@Greg I'm gonna need you to put something here}

>>>>

To collect our data for package usage in public projects, 
we turned to the Google BigQuery \code{github\_repos} data 
set\footnote{https://bigquery.cloud.google.com/dataset/bigquery-public-dat:github\_repos}.
From this data, we skimmed all projects and pulled those 
written in JavaScript, resulting in an initial total of 9,017,221 
repositories. Simply being written in JavaScript is not enough to detect
\code{npm} usage, so to find repositories using \code{npm} packages
we looked for projects that contained a \code{package.json} 
file. After confirming that the formatting of the file matched the \code{npm}
standard, we are able to confidently say that any remaining packages are 
using \code{npm} packages. With this criteria, we then compiled a list 
of [100,000 for now] project 
repositories from GitHub, a volume that we felt is likely to be an 
appropriate representation of all such public projects.
Using the \code{GitHub} platform API and the list of valid repository names 
from before, we cloned the GitHub repository for each project. With
this, we were then able to determine the date and time of every 
commit of the project, as well as the list of included \code{npm} packages
at the time of commit, as listed in every commit version of 
\code{package.json}. The results showed that on average a repository 
had 37.9 commits as well as [STATS HERE]. Ultimately, of the 9,017,221 
public \code{GitHub} projects written in JavaScript and the [NUMBER] of repositories
using \code{npm} packages, we randomly selected [NUMBER] repositories as
a representative data set for the analysis.
